Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-01-10 paper/introduction.tex
Fix GitHub typo

This paper details another example of \saw\ verification only this time it is a proof showing the \openssl\ C implementation of \shaThree\ matches a \cryptol\ specification derived from the published \fips\ standard by \nist\ \cite{fips202}.
The \cryptol\ specifications, \saw\ scripts, and extracted \sawcore\ model from the \openssl\ C implementation are documented, and available, in a public Github repository for independent verification \cite{repo}.
The proof relies on two specifications, both created as part of this research, of the \shaThree\ algorithm: one that closely matches the published standard and another incorporating features in the C implementation.
\saw\ shows an input to output equivalence between these two specifications for the 256 bit digest over a fixed set of message sizes. The proof takes around 60 hours of computation time.

>>>>

This paper details another example of \saw\ verification only this time it is a proof showing the \openssl\ C implementation of \shaThree\ matches a \cryptol\ specification derived from the published \fips\ standard by \nist\ \cite{fips202}.
The \cryptol\ specifications, \saw\ scripts, and extracted \sawcore\ model from the \openssl\ C implementation are documented, and available, in a public GitHub repository for independent verification \cite{repo}.
The proof relies on two specifications, both created as part of this research, of the \shaThree\ algorithm: one that closely matches the published standard and another incorporating features in the C implementation.
\saw\ shows an input to output equivalence between these two specifications for the 256 bit digest over a fixed set of message sizes. The proof takes around 60 hours of computation time.
